---
title: "Share data as pins with Dropbox"
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To share different versions of an evolving dataset we can use the
[pins](https://pins.rstudio.com/) package and Dropbox.

### Publish

```{r child="publish-pins.Rmd", include=FALSE}

```

### Use

* You have the shared Dropbox folder locally in your computer and in sync.

* Use the [pins](https://pins.rstudio.com/) package. For convenience I also use the packages tidyverse, here, and a custom function `pins_path()`.

* Define the pins board you'll use.

```{r}
library(pins)
library(tidyverse, warn.conflicts = FALSE)
library(here)

source(here("R", "pins_path.R"))

pins_path()
board <- board_folder(pins_path())
```

* Read the latest version of a pin.

```{r}
board %>% 
  pin_read("esa_sme")
```

* List all pins published into the shared board.

```{r}
board %>% 
  pin_list()
```

* Explore the available versions of one specific dataset.

```{r}
versions <- board %>% 
  pin_versions("esa_sme")

versions
```

* Explore the metadata for a version of a pin.

```{r}
version <- versions %>% 
  # These functions come from the tidyverse
  slice(2) %>% 
  pull(version)

version

board %>% 
  pin_meta("esa_sme", version)
```

* Read a specific version.

```{r}
board %>% 
  pin_read("esa_sme", version)
```
